### 2015-05-19 writing/SNLI paper/corpus.tex
Paper update.

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{7.5cm}lp{5.5cm}}
  \toprule
A young man in a striped hoodie looks at an artistic Levi's advertisement that says "We are all workers." & \ii{entailment} & There is a man in a hoodie looking at an advertisement.\\
\rule{0pt}{3ex}Two men on laptops in a dark room. & \ii{entailment} & Two men are on their laptops.\\
\rule{0pt}{3ex}A naked baby and toddler smear each other in paint. & \ii{neutral} & The kids are in the bathtub.\\
\rule{0pt}{3ex}A woman is focusing on her game of curling. & \ii{neutral} & There is a women playing a game indoors\\
\rule{0pt}{3ex}A group of people dressed in green and white are dancing in a circle outside of a white building. & \ii{contradiction} & A group performs indoors.\\
\rule{0pt}{3ex}A balding professor giving a lecture to students on the topic of "opportunity". & \ii{neutral} & A female professor with hair giving a lecture to students.\\
% TODO: Replace with *validated* examples from the post-rc2 training set, include all 5 labels
    \bottomrule
% From 1.0rc2
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from SNLI.}
\end{table*}

\subsection{The distributed corpus}

>>>>

\subsection{The distributed corpus}
\todo{Update all statistics to reflect the latest relase candidate.}

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{7.5cm}lp{5.5cm}}
  \toprule
A young man in a striped hoodie looks at an artistic Levi's advertisement that says "We are all workers." & \ii{entailment} & There is a man in a hoodie looking at an advertisement.\\
\rule{0pt}{3ex}Two men on laptops in a dark room. & \ii{entailment} & Two men are on their laptops.\\
\rule{0pt}{3ex}A naked baby and toddler smear each other in paint. & \ii{neutral} & The kids are in the bathtub.\\
\rule{0pt}{3ex}A woman is focusing on her game of curling. & \ii{neutral} & There is a women playing a game indoors\\
\rule{0pt}{3ex}A group of people dressed in green and white are dancing in a circle outside of a white building. & \ii{contradiction} & A group performs indoors.\\
\rule{0pt}{3ex}A balding professor giving a lecture to students on the topic of "opportunity". & \ii{neutral} & A female professor with hair giving a lecture to students.\\
    \bottomrule
% From 1.0rc2`
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from SNLI.\\
\todo{Replace with *validated* examples from the post-rc2 training set, include all 5 labels.}}
\end{table*}

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development sent with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and bare noun phrases of a style that is appropriate for the underlying caption task. Punctution and capitalization are only intermittently present.

### 2015-05-19 writing/SNLI paper/transfer.tex
Paper update.

We argue that for a sentence representation to provide the information necessary to reliably perform NLI classification, it must contain a faithful and thorough description of the sentence's meaning. This claim has a readily testable consequence: the knowledge that a representation learning system learns when it is trained on SNLI should transfer well to any other task that involves understanding sentence meaning. To test this, we perform transfer learning experiments on four other tasks, in which models are initialized using the parameters of a model trained on  on SNLI (as in \S\ref{sentence-embedding}) and then trained to convergence on the target tasks.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{2}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer}  \\
\hline
\t{SICK}            & \t{98} & \t{95} & \t{65?} & \t{68?}  \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{FactBank?}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:transferresults}
LSTM
\todo{numbers are approx.}
}
\end{table}

>>>>

We argue that for a sentence representation to provide the information necessary to reliably perform NLI classification, it must contain a faithful and thorough description of the sentence's meaning. This claim has a readily testable consequence: the knowledge that a representation learning system learns when it is trained on SNLI should transfer well to any other task that involves understanding sentence meaning. To test this, we perform transfer learning experiments on four other tasks, in which models are initialized using the parameters of an LSTM RNN-based model trained on  on SNLI (as in \S\ref{sentence-embedding}) and then trained to convergence on the target tasks.

We first evaluate on SICK (\citealt{marelli2014sick}), the smaller entailment corpus SNLI was modeled on, training on the standard 4.5k training sentence pairs. We then evaluate on SUBJ (\citealt{pang2004sentimental}), a two-way sentence classification task, using 5-fold cross-validation over the 10k sentences. We next evaluate on the SST (\citealt{socher2013acl1}), a five-way sentiment classification task with labels for both phrases and sentences. We train on both types of label within the 8.5k sentence training set and test on only the sentence-level labels in the test set. We finally evaluate on FactBank. \todo{FactBank} ....

 For SICK, we use pretrained parameters for all of the LSTM parameters, pretrained parameters for the $\tanh$ layers in the classifier, and pretrained embeddings for all of the words that occurred in both corpora, randomly initializing only the softmax layer and the remaining word embeddings. We use a similar strategy for the other three tasks, but do not transfer the initialization for the $\tanh$ layers, since the switch between sentence pair classification (in SNLI) and single sentence classification means that the input sizes for the bottom $\tanh$ do not match. In both cases we re-initialize AdaDelta as for a new model run.

\todo{Do we want to use all four target tasks?}

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{2}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer}  \\
\hline
\t{SICK}            & \t{98} & \t{95} & \t{65?} & \t{68?}  \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{FactBank?}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{\label{tab:transferresults}
The performance of an LSTM RNN classification model on four tasks under both a random initialization and an initialization copied from a model trained on SNLI.
\todo{Fill in numbers.}}
\end{table}

The results are shown in Table~\ref{tab:transferresults}. For each task, the transfer model is compared with a model that was initialized randomly as normal. Note that \todo{something interesting happens}. Our transfer model shows \todo{something about the state of the art on the tasks.}
